Manuscript drafts

### 2020-04-04 datasets/data_preprocessing.nb.Rmd
add id to datadd id to datasets

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
This notebook processes all systematic review datasets into datasets suitable testing asreview.

Every dataset is a .csv file with the following columns: 
  - title
  - abstract
  - label_included
  - keywords? (?)

@@

# remove missing abstracts 
nudging_test <- n_raw %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "", abstract != "NA") %>%
  distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts

@@

```{r}
# finalize dataset  
ptsd_test <- ptsd_test %>%
  select(authors, title, abstract, keywords, included, inclusion_code) # select relevant columns

@@

### Creating test dataset
```{r}
hall_test <- hall_asr %>%
   drop_na(abstract) %>% # drop entries with missing abstracts
   filter(abstract != "") %>%
   distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts

@@

# save datafile, to serve as data for descriptive table in manuscript
save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")

@@

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")) %>% 
  t() %>% 
  kable("html") %>%
  kable_styling(full_width = TRUE) %>%
  #scroll_box(width = "100%", height = "200px") %>%
  pack_rows("Paper", 2, 5) %>%
  pack_rows("Raw data", 6, 9) %>%
  pack_rows("ASReview data", 10, 13) %>%
  pack_rows("Test data set", 14, 17)  
```

Descriptives on missingness and duplicate abstracts in the ASReview test data set. 
```{r, echo = FALSE}
drops %>%
  kable("html",
        col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
        digits = 2) %>%
  kable_styling(full_width = TRUE)

@@

# Write all test dataset files 
```{r, eval = FALSE}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, keywords, label_included), "test_datasets/ace.csv")

# nudging (no keywords available)
write.csv(nudging_test %>% select(title, abstract, included), "test_datasets/nudging.csv")

# ptsd
write.csv(ptsd_test %>% select(authors, title, abstract, keywords, included), "test_datasets/ptsd.csv")

# hall (no keywords available )
write.csv(hall_test, "test_datasets/software.csv")

# virus 
write.csv(v_test %>% select(authors, title, abstract, keywords, included), "test_datasets/virus.csv")

# wilson
write.csv(w_test %>% select(authors, title, abstract, keywords, included), "test_datasets/wilson.csv")
```

# write test dataset files for simulation (removing keywords)
```{r, eval = FALSE}
# ace
write.csv(ace_test %>%  select(authors, title, abstract, label_included), "sim_datasets/ace.csv")
# nudging (no keywords available)
write.csv(nudging_test %>% select(title, abstract, included), "sim_datasets/nudging.csv")
# ptsd
write.csv(ptsd_test %>% select(authors, title, abstract, included), "sim_datasets/ptsd.csv")
# hall (no keywords available )
write.csv(hall_test, "sim_datasets/software.csv")
# virus 
write.csv(v_test %>% select(authors, title, abstract, included), "sim_datasets/virus.csv")
# wilson
write.csv(w_test %>% select(authors, title, abstract, included), "sim_datasets/wilson.csv")
```

>>>>

---
title: "Dataset preprocessing"
output: github_document
---
This notebook processes all systematic review datasets into datasets suitable testing ASReview.

Every dataset is a .csv file with the following columns: 
  - title
  - abstract
  - label_included
  - keywords? (only for hyperparameter optimization, not for simulation).

@@

# remove missing abstracts 
nudging_test <- n_raw %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  filter(abstract != "", abstract != "NA") %>%
  distinct(abstract, .keep_all = TRUE) %>% # remove entries with duplicate abstracts
  mutate(id = X)

@@

```{r}
# finalize dataset  
ptsd_test <- ptsd_test %>%
  select(id, authors, title, abstract, keywords, included, inclusion_code) # select relevant columns

@@

### Creating test dataset
```{r}
hall_test <- hall_asr %>%
   drop_na(abstract) %>% # drop entries with missing abstracts
   filter(abstract != "") %>%
   distinct(abstract, .keep_all = TRUE) # remove entries with duplicate abstracts

hall_test <- hall_test %>% # add id
  mutate(id = 1:nrow(hall_test))

@@

# save datafile, to serve as data for descriptive table in manuscript
saveRDS(all, file = "data_statistics/all.RDS")

@@

       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       `fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")) %>% 
  t() %>% 
  kable("markdown") 
# %>%
#   kable_styling(full_width = TRUE) %>%
#   #scroll_box(width = "100%", height = "200px") %>%
#   pack_rows("Paper", 2, 5) %>%
#   pack_rows("Raw data", 6, 9) %>%
#   pack_rows("ASReview data", 10, 13) %>%
#   pack_rows("Test data set", 14, 17)  
```

Descriptives on missingness and duplicate abstracts in the ASReview test data set. 
```{r, echo = FALSE}
drops %>%
  kable("markdown",
        col.names = c("n", "NA", "NA rate (%)", "duplicates", "duplicate rate (%)"),
        digits = 2) 
# %>%
#   kable_styling(full_width = TRUE)

@@

# Write all test dataset files 
```{r, eval = TRUE}
# ace
write.csv(ace_test %>%  select(pubmedID, authors, title, abstract, keywords, label_included), "test_datasets/ace.csv", row.names = FALSE)

# nudging (no keywords available)
write.csv(nudging_test %>% select(id, title, abstract, included), "test_datasets/nudging.csv", row.names = FALSE)

# ptsd
write.csv(ptsd_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/ptsd.csv", row.names = FALSE)

# hall (no keywords available )
write.csv(hall_test, "test_datasets/software.csv", row.names = FALSE)

# virus 
write.csv(v_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/virus.csv", row.names = FALSE)

# wilson
write.csv(w_test %>% select(id, authors, title, abstract, keywords, included), "test_datasets/wilson.csv", row.names = FALSE)
```

# write test dataset files for simulation (removing keywords)
```{r, eval = TRUE}
# ace
write.csv(ace_test %>%  select(pubmedID, title, abstract, label_included), "sim_datasets/ace.csv", row.names = FALSE)
# nudging (no keywords available)
write.csv(nudging_test %>% select(id, title, abstract, included), "sim_datasets/nudging.csv", row.names = FALSE)
# ptsd
write.csv(ptsd_test %>% select(id, title, abstract, included), "sim_datasets/ptsd.csv", row.names = FALSE)
# hall (no keywords available )
write.csv(hall_test, "sim_datasets/software.csv", row.names = FALSE)
# virus 
write.csv(v_test %>% select(id, title, abstract, included), "sim_datasets/virus.csv", row.names = FALSE)
# wilson
write.csv(w_test %>% select(id, title, abstract, included), "sim_datasets/wilson.csv", row.names = FALSE)
```

### 2020-04-04 manuscript/drafts/manuscript.Rmd
add id to datadd id to datasets

  M = train($\mathcal{L}$)
  query x \isin

@@

## Datasets

The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

The raw datafiles published with the SRs were preprocessed into a test dataset.
The test datasets contain title information on all citations obtained in the search strategy. 
The instances in the data consist of a title, an abstract and were labeled to indicate which citations were included in the systematic review. 
Instances with missing abstracts were removed. 
Duplicate instances were removed. 
Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]

@@

For example $M_1$ BTMD (naive bayes, tfidf, certainty sampling, double balance)
STMD

@@

#### The next abstract to be queried  
The model has various ways of deciding which instance should be queried next.

@@

#### Starting point
The initial training set consists of 5 inclusions and 5 exclusions, randomly sampled from the dataset. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.

```
c = naivebayes
f = tfidf
q = max
n_prior_included = 5
n_prior_excluded = 5
```

#### Retraining
We can choose to retrain the model after labeling $n$ instances. 
- n_instances=10 (number of papers each query)

## Simulations
To evaluate performance of the five models described above, the model is used to simulate five existing systematic reviews. 
A simulation is of one model on one dataset. 
The simulation is repeated for 15 trials $t$.

@@

>>>>

  M = train($\mathcal{L}$)
  Query x \isin \mathcal{U} (<x, y=?)
  oracle <x, y>

@@

@@

For example $M_1$ BCTD (naive bayes, certainty sampling, tf-idf, dynamic supersampling)
STMD

@@

#### The next abstract to be queried  
The model has various ways of deciding which instance should be queried next. 
(C) but other methods, here only C

@@

Dynamic Supersampling (D)

## Simulations
A simulation is of one model on one dataset. 
The simulation is repeated for 15 trials $t$.

@@

#### Controlled Variables
Starting point
The initial training set consists of 1 inclusion and 1 exclusion, randomly sampled from the dataset. 
Demonstrate 'worst case scenario' where reviewer has minimal prior knowledge on publications in the data. 
The researcher has some prior knowledge about the pool, some papers ought to be included in the SR.

Retraining
We can choose to retrain the model after labeling $n$ instances. 
- n_instances=1 (number of papers each query)

## Datasets
Six Systematic Reviews from various research areas were used to simulate the automated systematic review process.
The data from the original source were preprocessed into a test dataset, containing all publications obtained in the systematic search, with labels indicating the publications included in the systematic review.

The test datasets contain title information on all publications obtained in the search strategy. 
The instances in the data consist of a title, an abstract and were labeled to indicate which publications were included in the systematic review. 
Instances with missing abstracts were removed. 
Duplicate instances were removed. 
Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]

test datasets serve as systematic search results, then perform active learning to detect inclusions.
